Empirical Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-02-18 written/paper.tex
written

\section{Introduction}
On 10 January 2024, the United States Securities and Exchange Commission approved the listing and trading of a range of spot bitcoin exchange-traded product (ETP) shares (Gensler, 2024). In other markets, structured products in Bitcoin (and other crypto assets) have been available for years and retailers have been able to mine or buy it since its inception following Nakamoto, 2009. 
Yet, despite the ongoing integration into established markets, fundamental questions about crypto asset markets remain unclear:
How efficient are crypto asset markets relative to established, traditional markets such as equities? 
Does a risk-free rate exist and if yes, how does it relate to the risk-free rate in established markets? Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives? 
We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s. 
The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway et al. (2000) and Kapadia et al. (2001).

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. The proxy serves as a benchmark that beta-neutral portfolios should yield. 
Subsequently, we construct and evaluate the performance of beta-neutral option portfolios using a unique data set of executed transactions from Derbit, the largest Crypto Options Exchange.  We find that the beta-neutral option portfolios, written on Bitcoin and Ether, are fairly priced for most levels of moneyness. However, the portfolios do not generate the appropriate theoretical returns for at-the-money instruments. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Kapadia et al. (2001) and Shumway et al. (2000), the existence of high premia.for at-the-money options. The effect holds after compensating for tail risk (market crash insurance) and transaction cost.

@@

In order to apply concepts of mathematical finance onto crypto assets, it is paramount to develop a risk-free rate - or at least a low-risk rate whose residual risk may converge to zero in time. 
An interesting candidate for a low-risk bond in the crypto asset space would be staking, which is the validation of transactions under the risk of losing a principal (the stake). Evidently, only crypto assets which follow a Proof-of-Stake (PoS) consensus mechanism instead of a Proof-of-Work (PoW) consensus mechanism can be used for staking. At the time, this is still a minor amount of cryptocurrencies. We include one of those, Ether, in our experiment. However, we figure that a multitude of risks is still present in staking, such as the risk of hacks, software bugs, slashing or blockchain congestions and subsequent reduction of stakes.
Another approach to develop a risk-free rate would be lending in the DeFi space. Yet, this space may be vulnerable to similar risks as staking through hacks or software bugs in smart contracts.

In the absence of riskless bond, we construct as a proxy for the risk free rate via the replication of the market-implied yield through a position in futures contracts, whose risks mainly arise due to liquidity risk and counterparty risk.
A large share of the trading volume in digital asset markets falls on the futures market. Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments. As depicted in Table \ref{table:stats}, measured by the aggregate open interest and aggregate trading volume the market share of Perpetual Futures dwarfs the market share of (classic) Futures for both, Bitcoin and Ether. While it would be possible to use a yield from a long-short futures position (e.g. short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration.

Solve for interest rates from (classic) Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:

@@

We follow the argument that any beta-neutral portfolio should yield the risk-free rate. We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero. The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$. The weight $\theta$ is found by solving Equation 2 through Equation 3. The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4. 
The underlying data are executed transactions. All option greeks remain constant except time-to-maturity. Any transaction has a time-to-maturity $\tau$ adjusted so that it would coincide with settlement time. All options are bought and held until settlement at 10am UTC. 
We match our universe of straddles as follows:
Per definition, a straddle exists of a call and a put with similar strike and maturity. We construct the set of empirical straddles by iterating over our list of executed calls and puts. For each call (put), we use Put-Call-Parity to complete the straddle. 
The empirical performance of the resulting zero-beta straddles is assessed on a daily base. We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed. For each level of moneyness $m$, we construct an interval $[m, m + 0.05]$. We condition daily returns on levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero. We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.

@@

We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events. Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles. 
Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility. This premium more than empirically justified, but we choose the size due to the possibility of illiquidity for OTM contracts and the intention to enter both legs of the straddle simultaneously.
%Maybe make a summary of the relationship between ATM and 20\% OTM premium.

@@

Considering data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
The most likely negative factor that could affect our data quality is wash trading. 
We follow the definition of XPYZ on wash trading (from: ):
"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." ()

We asses the overall risk of wash trading contaminating our data set as low. The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost. At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot of 51,765 USD results in a fee of 15.5 USD. Such fees, even without consideration of spreads, make wash trading from a trader's perspective prohibitively expensive.

@@

Consequently, we find a similar result to Shumway et al. (2000) and Bakshi et al. (2001), namely is the existence of a premium for ATM contracts. Additionally, we find a similar premium for slightly ITM contracts.
Shumway et. al reported an average return of around -3.15 percent per week, whereas XYZ \% is attributable to the volatility premium.

@@

@@

Make bridge to interest rates

@@

\leavevmode\hypertarget{sec-approval}{}%
Gary Gensler, Chair of the United States Securities and Exchange Commission. Statement on the Approval of Spot Bitcoin Exchange-Traded Products (10 January 2024).
Available at \url{https://www.sec.gov/news/statement/gensler-statement-spot-bitcoin-011023}. Accessed 18 February 2023.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{winkel}{}%
Winkel, J and Härdle, WK, Pricing Kernels and Risk Premia implied in Bitcoin Options (November 21, 2022).Available at SSRN: \url{https://ssrn.com/abstract=4282905} or \url{http://dx.doi.org/10.2139/ssrn.4282905}.

@@

%\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021

@@

%\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}    & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
\# Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
\# Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
\# BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
\# Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
\# Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
\# Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
\# Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
\# Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
\# OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
\# Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31                        
\end{tabular}}
\caption{Bitcoin Perpetual Futures. Source: Coingecko.}
\label{table:btc_perpetuals}
\end{table}

\begin{table}[ht]
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30                     
\end{tabular}}
\caption{Ether Perpetual Futures. Source: Coingecko.}
\label{eth_perpetual_futures}
\end{table}

@@

\# Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
\# Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
\# Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
\# Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
\# BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
\# BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
\# BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
\# BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
\# BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
\# BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
\# BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
\# BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
\# Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
\# Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
\# Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
\# Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
\# Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
\# Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
\# Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\

>>>>

\section{Introduction}
On 10 January 2024, the United States Securities and Exchange Commission approved the listing and trading of a range of spot bitcoin exchange-traded product (ETP) shares (Gensler, 2024). In other markets, structured Bitcoin (BTC) products have been available for years and retailers have been able to mine or buy Bitcoin since its inception following Nakamoto, 2009. 
Yet, despite the ongoing integration into established markets, fundamental questions about crypto asset markets remain unclear:
How efficient are crypto asset markets relative to established, traditional markets such as equities? 
Does a risk-free rate exist and if yes, how does it relate to the risk-free rate in established markets? Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives? 
We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 1990s. 
The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway et al. (2000) and Kapadia et al. (2001).

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. The proxy serves as a benchmark that beta-neutral portfolios should yield. 
Subsequently, we construct and evaluate the performance of beta-neutral option portfolios using a unique data set of executed transactions from Derbit, the largest Crypto Options Exchange.  We find that the beta-neutral option portfolios, written on Bitcoin and Ether, are fairly priced for most levels of moneyness. However, the portfolios do not generate the appropriate theoretical returns for at-the-money instruments. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Kapadia et al. (2001) and Shumway et al. (2000), the existence of high premia for at-the-money options. The effect holds after compensating for tail risk (market crash insurance) and transaction cost.

@@

In order to apply concepts of mathematical finance onto crypto assets, it is paramount to develop a risk-free rate - or at least a low-risk rate whose residual risk may converge to zero in time. 
An interesting candidate for a low-risk bond in the crypto asset space would be staking, which is the validation of transactions under the risk of losing a principal (the stake). Evidently, only crypto assets which follow a Proof-of-Stake (PoS) consensus mechanism instead of a Proof-of-Work (PoW) consensus mechanism can be used for staking. At the time, this is still a minor share of the crypto asset universe. We include one of those, Ether, in our experiment. However, we figure that a multitude of risks is still present in staking, such as the risk of hacks, software bugs, slashing or blockchain congestions and subsequent reduction of stakes.
Another approach to develop a risk-free rate would be lending in the DeFi space. Yet, this space may be vulnerable to similar risks as staking through hacks or software bugs in smart contracts.

In the absence of riskless bond, we construct as a proxy for the risk free rate via the replication of the market-implied yield through a position in futures contracts, whose risks mainly arise due to liquidity risk and counterparty risk.
A large share of the trading volume in digital asset markets falls on the futures market. Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments. As depicted in Table \ref{table:stats}, measured by the aggregate open interest and aggregate trading volume the market share of Perpetual Futures dwarfs the market share of (classic) Futures for both, Bitcoin and Ether. While it would be possible to use a yield from a long-short futures position (e.g. short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration. 
Solve for interest rates under observale Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:

@@

We follow the argument that any beta-neutral portfolio should yield the risk-free rate. We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero. The straddle's payoff $r_v$ is depicted in Equation 4, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$. The weight $\theta$ is found by solving Equation 5 through Equation 6. The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\Delta$, the Black-Scholes option price $C$ as depicted in Equation 7. % and the market beta $\beta_m (=1)$
The underlying data are executed transactions. All option greeks remain constant except time-to-maturity. Any transaction has a time-to-maturity $\tau$ adjusted so that it would coincide with settlement time. All options are bought and held until settlement at 10am UTC. 
We match our universe of straddles as follows:
Per definition, a straddle exists of a call and a put with similar strike and maturity. We construct the set of empirical straddles by iterating over our list of executed calls and puts. For each call (put), we use Put-Call-Parity to complete the straddle. 
The empirical performance of the resulting zero-beta straddles is assessed on a daily base. We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed. For each level of moneyness $m$, we construct an interval $[m, m + 0.05]$. We condition daily returns on levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero. We define a measurable non-zero return on a 95\% significance level of the zero-beta straddle returns as (volatility) risk premium.

@@

We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events. Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles. 
In order to exclude influence of Fat Tail Events, we hedge the straddle with far-out-the-money (FOTM) options. This results in a so-called "Reverse Iron Butterfly Spread", whose risk is limited to the sum of option premia.
We close the Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility. This premium more than empirically justified, but we choose the size due to the possibility of illiquidity for OTM contracts and the intention to enter both legs of the straddle simultaneously.
%Maybe make a summary of the relationship between ATM and 20\% OTM premium.

@@

Regarding matters of data authenticity, we refer to our previous paper regarding the study of Bitcoin option data (Winkel and Härdle, 2023).
The most likely negative factor that could affect our data quality is wash trading. 
We follow the definition of Intercontinental Exchange, Inc. (2001): "A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery."
We asses the overall risk of wash trading contaminating our data set as low. The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost. At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot of 51,765 USD results in a fee of 15.5 USD. Such fees, even without consideration of spreads, make wash trading from a trader's perspective prohibitively expensive.

@@

Consequently, we find a similar result to Shumway et al. (2000) and Bakshi et al. (2001), namely is the existence of a premium for ATM contracts. Additionally, we find a similar premium for slightly ITM contracts.
Shumway et. al reported an average return of around -3.15\% per week.% whereas XYZ \% is attributable to the volatility premium.

@@

Evidently, these large, negative returns are neither explainable by the interest rate proxy via the perpetual futures nor government bonds.

@@

@@

\leavevmode\hypertarget{sec-approval}{}%
Gary Gensler, Chair of the United States Securities and Exchange Commission. Statement on the Approval of Spot Bitcoin Exchange-Traded Products (10 January 2024).
\url{https://www.sec.gov/news/statement/gensler-statement-spot-bitcoin-011023}. Accessed 18 February 2023.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{winkel}{}%
Winkel, J. and Härdle, W.K. Pricing Kernels and Risk Premia implied in Bitcoin Options. Risks 2023, 11, 85. Available at \url{https://doi.org/10.3390/risks11050085}.

@@

%\url{https://www.deribit.com/main/insurance}. Accessed 4 January 2021

@@

%\url{https://www.deribit.com/main/indexes}. Accessed 2 January 2021

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}    & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
 Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
 Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
 BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
 Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
 Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
 Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
 Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
 Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
 OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
 Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31                        
\end{tabular}}
\caption{Bitcoin Perpetual Futures. Source: Coingecko.}
\label{table:btc_perpetuals}
\end{table}

\begin{table}[ht]
\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
\hline
\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\hline
\hline
 Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
 Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
 Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
 OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
 Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
 BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
 Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
 Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
 Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
 XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30                     
\end{tabular}}
\caption{Ether Perpetual Futures. Source: Coingecko.}
\label{eth_perpetual_futures}
\end{table}

@@

 Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
 Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
 Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
 Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
 BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
 BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
 BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
 BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
 BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
 BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
 BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
 BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
 Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
 Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
 Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
 Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
 Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
 Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
 Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\
 Bybit (Futures)               & BTC-26JAN24        & \$44,370.24                        & 44042.75 USDC                            & -0.773\%                           & 0.02\%                              & 19 days                                 & -                                          & \$47,245.15                             \\
 Bybit (Futures)               & BTC-23FEB24        & \$44,806.59                        & 44042.99 USDC                            & -1.739\%                           & 0.03\%                              & about 2 months                          & -                                          & \$8,650.36                              \\
